### 2017-10-24 paper/sexSelectionSpacing-ver1.tex
Minor edits

To provide a first look at how the hypothese holds up, Tables 
\ref{tab:median_sex_ratio_low},
\ref{tab:median_sex_ratio_med}, and
\ref{tab:median_sex_ratio_high}
show predicted median duration and sex ratios for the three different
education levels by spell, sex composition, and periods.
These predictions are based on the estimation results employing the method 
detailed in Section \ref{sec:strategy} and are calculated using the means of 
the continuous explanatory variables and the majority category for categorical 
explanatory variables.
The median duration is the number of months it is predicted to take for
half of the women who are predicted to have a birth by the end of spell length
covered.
For example, if 80\% of women with a given set of characteristics are predicted to
have a birth by the end of the end of spell, the median duration is the number of
months it would take for 40\% of women to have a birth.
The sex ratio is the percent of births that result in a son, based on all the 
births predicted to happen over the spell.

@@

>>>>

To provide a first look at how the hypothese holds up, Tables 
\ref{tab:median_sex_ratio_low},
\ref{tab:median_sex_ratio_med}, and
\ref{tab:median_sex_ratio_high}
show predicted median duration and sex ratios for the three different
education levels by spell, sex composition, and periods.
These predictions are based on the estimation results employing the method 
detailed in Section \ref{sec:strategy} and are calculated using the means of 
the continuous explanatory variables and the majority category for categorical 
explanatory variables.
The median duration is the number of months it is predicted to take for
half of the women who are predicted to have a birth by the end of spell length
covered.
For example, if 80\% of women with a given set of characteristics are predicted to
have a birth by the end of the end of spell, the median duration is the number of
months it would take for 40\% of women to have a birth.
The sex ratio is the percent of births that result in a son, based on all the 
births predicted to happen over the spell.
If the estimations are based on 100 or fewer births in a cell the predictions
for that cell are not presented.
Furthermore, those cells with 500 or fewer births are marked.

@@

Table \ref{tab:median_sex_ratio_low} show the predictions for women with 
no education.
Overall, spacing is shorter the fewer boys a couple has, although the
differences in median duration are never more than 3 months and most
are only one or two months.%
\footnote{
This is ignoring those cells with few births.
}
Furthermore, there is little change across the 3 periods.
This is consistent with an absence of sex-selective abortions for
this group of women.
